---
title: "WKCLIMAD Network Models"
author: 
output:
  pdf_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    highlight: tango
    keep_tex: yes
    latex_engine: xelatex
    toc: TRUE
  word_document:
    fig_caption: yes
    fig_width: 4
    keep_md: yes
  header-includes:
  - \usepackage{inputenc}
  - \usepackage{unicode-math}
  - \pagenumbering{gobble}
  html_document:
    includes:
      after_body: Figs/ChordPlot.html
    df_print: kable
    fig_caption: yes
    theme: flatly
    toc: true
    toc_float: true
---

```{r startup, eval=TRUE, echo=FALSE, results='hide',message=FALSE}

suppressMessages(suppressWarnings(source("R/make.R")  ))     # loads packages, data, setup, etc.
knitr::opts_chunk$set(echo = T, fig.align="center")
thisYr <- format(Sys.time(), "%Y")
today  <- format(Sys.time(), "%b %d, %Y")
tmstp  <- format(Sys.time(), "%Y_%m_%d")
```


# 1. WKCLIMAD Overview

This repository contains R code and Rdata files for working with WKCLIMAD data and responses. WKCLIMAD is an ICES workshop aimed at exploring how can the short-, medium-, and long-term influences of climate change on aquaculture, fisheries, and ecosystems be accounted for in ICES Advice.

More information about WKCLIMAD can be found here:https://www.ices.dk/community/groups/Pages/WKCLIMAD.aspx


# 2. Visualizing the results

The interactive shiny() is downloadable by entering the following lines of code into R().


```{r model1, echo=T, include=T, eval=F,message=F}
#'Run the WKCLIMAD results
#'
#'https://github.com/kholsman/WKCLIMAD

missing <- setdiff("shiny", installed.packages()[, 1])
if (length(missing) > 0) install.packages(missing)

# Load libraries:
for(lib in c("shiny"))
  suppressMessages(eval(parse(text=paste("library(",lib,")"))))

runGitHub( "WKCLIMAD", "kholsman")


```

<!-- ![demographics map]('Figs/ChordPlot.html') -->
<!-- ```{r sfint-shiny} -->
<!-- knitr::include_app("https://kkh2022.shinyapps.io/WKCLIMAD/",  -->
<!--   height = "900px") -->
<!-- ``` -->
## 3. Chord Diagram

```{r showChoro1,eval=T,echo=F}
htmltools::includeHTML("Figs/ChordPlot.html")
```
<!-- ```{r showChoro1,echo=F} -->
<!-- # All defaults -->
<!-- htmltools::includeHTML("Figs/ChordPlot.html") -->
<!-- # include_graphics("Figs/ForcePlot.html") -->
<!-- ``` -->

## 4. Force Diagram

<!-- ```{r showChoro2,echo=F} -->
<!-- htmltools::includeHTML("Figs/ForcePlot.html") -->
<!-- ``` -->

## 5. Sankey Diagram

<!-- ```{r showChoro3,echo=F} -->
<!--  htmltools::includeHTML("Figs/SankeyPlot.html") -->
<!-- ``` -->

```{r makeReadME, echo=FALSE,eval=F, include =F}

# copy and paste this into R window (won't work within markdown)
rmd2md(rmd_fl = "WKCLIMAD_readme",md_fl = "README")

```

