---
title: "WKCLIMAD Network Models"
author: 
output:
  pdf_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    highlight: tango
    keep_tex: yes
    latex_engine: xelatex
    toc: TRUE
  word_document:
    fig_caption: yes
    fig_width: 4
    keep_md: yes
  header-includes:
  - \usepackage{inputenc}
  - \usepackage{unicode-math}
  - \pagenumbering{gobble}
  html_document:
    includes:
      after_body: Figs/ChordPlot.html
    df_print: kable
    fig_caption: yes
    theme: flatly
    toc: true
    toc_float: true
---

```{r startup, eval=TRUE, echo=FALSE, results='hide',message=FALSE}

suppressMessages(suppressWarnings(source("R/make.R")  ))     # loads packages, data, setup, etc.
knitr::opts_chunk$set(echo = T, fig.align="center")
thisYr <- format(Sys.time(), "%Y")
today  <- format(Sys.time(), "%b %d, %Y")
tmstp  <- format(Sys.time(), "%Y_%m_%d")
```


# 1. WKCLIMAD Overview

This repository contains R code and Rdata files for working with WKCLIMAD data and responses. WKCLIMAD is an ICES workshop aimed at exploring how can the short-, medium-, and long-term influences of climate change on aquaculture, fisheries, and ecosystems be accounted for in ICES Advice.

More information about WKCLIMAD can be found here:https://www.ices.dk/community/groups/Pages/WKCLIMAD.aspx


# 2. Visualizing the results

The interactive shiny() is downloadable by entering the following lines of code into R().


```{r model1, echo=T, include=T, eval=F,message=F}
#'Run the WKCLIMAD results
#'
#'https://github.com/kholsman/WKCLIMAD

missing <- setdiff("shiny", installed.packages()[, 1])
if (length(missing) > 0) install.packages(missing)

# Load libraries:
for(lib in c("shiny"))
  suppressMessages(eval(parse(text=paste("library(",lib,")"))))

runGitHub( "WKCLIMAD", "kholsman")


```

<!-- ![demographics map]('Figs/ChordPlot.html') -->
<!-- ```{r sfint-shiny} -->
<!-- knitr::include_app("https://kkh2022.shinyapps.io/WKCLIMAD/",  -->
<!--   height = "900px") -->
<!-- ``` -->
## 3. Chord Diagram

```{r showChoro1,eval=T,echo=F}
htmltools::includeHTML("Figs/ChordPlot.html")
```
<!-- ```{r showChoro1,echo=F} -->
<!-- # All defaults -->
<!-- htmltools::includeHTML("Figs/ChordPlot.html") -->
<!-- # include_graphics("Figs/ForcePlot.html") -->
<!-- ``` -->
```{r plotChord,eval-F,echo=T}
  
  
  suppressMessages(source("R/packages.R"))      # loads packages
  suppressMessages(source("R/make.R"))
  
  
  input            <- list()
  input$modlist    <- models[6] 
  input$sinksRt    <- FALSE
  input$fontSize   <- 16
  input$vis_layout <- "layout_with_sugiyama"
  input$align_hier <- "no"
  input$dist       <- 100
  input$direction  <- "LR"
  input$minSize    <- 1
  input$labW = 20
 networks     <-  suppressWarnings(suppressMessages(
      plot_vis_network(
                                    modlistIN = input$modlist,
                                    fontSizeIN=input$fontSize,
                                    layoutIN =input$vis_layout,
                                    dirIN = input$direction,
                                    align_hierIN = input$align_hier,
                                    distIN =input$dist))) 
 
 
 
 
    network_vis   <- networks$vis
    network_force <- networks$force
    sankey        <- suppressMessages(plot_Sankey(modlistIN = input$modlist, 
                                                  sinksRightIN= input$sinksRt,
                                                  fontSizeIN=input$fontSize))
 network_force  # creates interactive network  
 network_vis    # creates vis network interactively
 sankey    # sankey diagram
 
    mod           <- networks$mod
    tree          <- suppressMessages(plot_tree(
                               modlistIN  = input$modlist,
                               saveIT     = F,
                               labW       = input$labW,
                               minSize    = input$minSize,
                               fontSizeIN = input$fontSize/2))
    tree
    chord         <- (suppressMessages(plot_chordDiag(
                           x           = input$modlist,
                           labW        = 20,
                           tblIN       = tbl,
                           tbl_metaIN  = tbl_meta,
                           links_allIN = links_all
      )))
    
    tt    <- suppressWarnings(suppressMessages(tmapCoords(
      modlistIN = input$modlist,
      minSize=input$minSize,
      fontSizeIN=input$fontSize/2)))
    tt<-tt%>%
      select(plotID,ymax,ymin,xmin,xmax )%>%
      mutate(area = (xmax-xmin)^2*(ymax-ymin)^2)
    tmapCoords_prcnt<-tt%>%
      mutate(percent = 100*area/sum(tt$area))%>%
      select(plotID,percent)
    
      plot_chordDiag2(x=models[6])
    sclr <- 1
    h <- 10*sclr
    w <- 10*sclr
    dpi <-350
    png(filename = "Figs/Chord2_fish.png",res=dpi, width = w,height =h, units="in")
    plot_chordDiag2(x=models[1:6])
    dev.off()
    
      png(filename = "Figs/Chord2_aqua.png",res=dpi, width = w,height =h, units="in")
    plot_chordDiag2(x=models[7:9])
    dev.off()
    
    png(filename = "Figs/Chord2_all.png",res=dpi, width = w,height =h, units="in")
    plot_chordDiag2(x=models)
    dev.off()
    
    sclr <- .5
    h <- 4*sclr
    w <- 10*sclr
    dpi <-350
    suppressMessages(plot_tree(modlistIN = models[1:6], 
                               file_name = "Figs/tree2_fish.png",
                               saveIT = T,width = w, height =h, dpi=dpi,
                               minSize=input$minSize,
                        fontSizeIN=input$fontSize/2))
    suppressMessages(plot_tree(modlistIN = models[6:9], 
                               file_name = "Figs/tree2_aqua.png",
                               saveIT = T,width = w, height =h, dpi=dpi,
                               minSize=input$minSize,
                        fontSizeIN=input$fontSize/2))
    
     suppressMessages(plot_tree(modlistIN = models, 
                                file_name = "Figs/tree2_all.png",
                               saveIT = T,width = w, height =h, dpi=dpi,
                               minSize=input$minSize,
                        fontSizeIN=input$fontSize/2))

    
    
 
  #     
  #      require(ComplexHeatmap)
  # 
  # 
  # # # discrete
  # # lgd_points = Legend(at = c("label1", "label2"), type = "points",
  # #                     legend_gp = gpar(col = 2:3), title_position = "topleft",
  # #                     title = "Track1")
  # # # discrete
  # lgd_lines = Legend(at = unique(meta_dat$lab), type = "lines",
  #                    legend_gp = gpar(
  #                      col = cc(length(unique(meta_dat$lab))), 
  #                      fontsize = 6,
  #                      lwd = 4), 
  #                    title_position = "topleft",
  #                    title = "Track2")
  # # # continuous
  # # lgd_links = Legend(at = c(-2, -1, 0, 1, 2), col_fun = cc,
  # #                    title_position = "topleft", title = "Links")
  # 
  # #lgd_list_vertical = packLegend(lgd_points, lgd_lines, lgd_links)
  # lgd_list_vertical = packLegend(lgd_lines)
  # 
  # draw(lgd_list_vertical, x = unit(4, "npc"), y = unit(100, "npc"), just = c("left", "bottom"))
  # 
  # # and a similar version of grid.draw
  # pushViewport(viewport(x = unit(1, "npc"), y = unit(0, "npc"), just = c("left", "bottom")))
  # grid.draw(lgd_lines)
  # popViewport()
  
    
  

```

## 4. Force Diagram

<!-- ```{r showChoro2,echo=F} -->
<!-- htmltools::includeHTML("Figs/ForcePlot.html") -->
<!-- ``` -->

## 5. Sankey Diagram

<!-- ```{r showChoro3,echo=F} -->
<!--  htmltools::includeHTML("Figs/SankeyPlot.html") -->
<!-- ``` -->

```{r makeReadME, echo=FALSE,eval=F, include =F}

# copy and paste this into R window (won't work within markdown)
rmd2md(rmd_fl = "WKCLIMAD_readme",md_fl = "README")

```

